Gravitational Lens Modelling in a Citizen Science Context

### 2014-09-22 text/ms.tex
typos and imgs

\author[Küng et al]{Rafael Küng,$^{1}$
Prasenjit Saha,$^{1}$
Anupreeta More,$^{2}$
Elisabeth Baeten,$^{3}$
\newauthor
Jonathan Coles,$^{4}$
Claude Cornen,$^{3}$
Christine Macmillan,$^{3}$
Phil Marshall,$^{5}$ 
\newauthor
Surhud More,$^{2}$
Jonas Odermatt,$^{6}$
Aprajita Verma$^{7}$
and Julianne Wilcox$^{3}$
%
\\
%
$^{1}$Physik-Institut, University of Zurich, 190 Winterthurerstrasse, 8057 Zurich, Switzerland\\
$^{2}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
$^{3}$The SpaceWarps Collaboration\\
$^{4}$Exascale Computing Lab, Versailles Saint-Quentin-en-Yveline University, 55 Avenue des Etats Unis, 78000, Versailles, France\\
$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
$^{6}$Kantonsschule Zug, L\"ussiweg 24, 6300 Zug, Switzerland\\
$^{7}$Oxford Astrophysics, Keble Road, Oxford OX1 3RH, UK\\
}

@@

The first post-modelling test was a qualitative comparison of the
original arrival-time surfaces and the input spaghetti diagrams given
by the modeller.  This tested first, for correct identification and
location of the lensed images, and second, the correct parities and
ordering for the lensed images in respect of the arrival time.

@@

\tabref{stats} presents a summary of the test.  The evaluation was
done manually, comparing the input to \spl with the actual
arrival-time surface of the sim.  This amounts to comparing the
upper-left and middle-left panels in each of
Figures~\ref{fig:6941}--\ref{fig:7022}, and similarly the other 111
models.

\begin{table}\centering\begin{tabular}{lrr}\hline
    Total & 119 &(100\%)\\
\hline
    errors in image locations  & 9 &(8\%)\\
    errors in image parities or time ordering & 49 &(41\%) \\
\hline
    inaccurate image placement over an arc & 21 &(18\%) \\
    identified two images of four & 5 &(4\%) \\
    identified two nearby images as one & 3 &(3\%) \\
    missed faint images & 1 &(1\%) \\
    proposed too many images & 1 &(1\%) \\
    modelled a three-image arc as one image & 4 &(3\%) \\
    modelled one image as a three-image arc & 5 &(4\%) \\
    swapped minimum and saddle in double  & 2 &(2\%) \\
    swapped minima and saddles in quad & 38 &(32\%)\\
    swapped early and late saddles in a quad & 7 &(6\%) \\
\hline
\end{tabular}
\caption{Table of image-identification errors and the number of models
  containing each.  A model can contain more than one type of error.}
\label{tab:stats}
\end{table}

@@

The assignment of the parity of the images was a more difficult task,
and was successful in only about 60\% of the cases.  The most common
error was swapping of minima and saddle-points in a quad;
\figref{7025} shows an example.  Another, less common, error was
flipping the spaghetti diagram, this swapping the time-ordering of the
two saddle points.

Incorrect image parities and time orderings tended to produce
poorer-looking models, such as the checkerboard patterns in the mass
map in \figref{7025}.  Interestingly, however, the enclosed-mass
profiles were quite robust.  We will consider this aspect in the next
section.

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/eR_5}
  \caption{Model-recovered versus actual Einstein radii \ERf[,rec] and
    \ERf[,act].
    Plus signs indicate models flagged by the modeller as
    failures by commenting negatively about it in the forum.}
  \label{fig:ER_per_sim}
\end{figure*}

>>>>

\author[Küng et al]{Rafael Küng,$^{1}$
Prasenjit Saha,$^{1}$
Anupreeta More,$^{2}$
Elisabeth Baeten,$^{3}$
\newauthor
Jonathan Coles,$^{4}$
Claude Cornen,$^{3}$
Christine Macmillan,$^{3}$
Phil Marshall,$^{5}$ 
\newauthor
Surhud More,$^{2}$
Jonas Odermatt,$^{6}$
Aprajita Verma$^{7}$
and Julianne K. Wilcox$^{3}$
%
\\
%
$^{1}$Physik-Institut, University of Zurich, 190 Winterthurerstrasse, 8057 Zurich, Switzerland\\
$^{2}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
$^{3}$The SpaceWarps Collaboration\\
$^{4}$Exascale Computing Lab, Versailles Saint-Quentin-en-Yveline University, 55 Avenue des Etats Unis, 78000, Versailles, France\\
$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
$^{6}$Kantonsschule Zug, L\"ussiweg 24, 6300 Zug, Switzerland\\
$^{7}$Oxford Astrophysics, Keble Road, Oxford OX1 3RH, UK\\
}

@@

The first post-modelling test was a qualitative comparison of the
original arrival-time surfaces and the input spaghetti diagrams given
by the modeller.  This tested first, for correct identification and
location of the lensed images, and second, for the correct parities and
ordering of the lensed images in respect of the arrival time.

@@

\tabref{stats} presents a summary of the test.  The evaluation was
done manually, comparing the input to \spl with the actual
arrival-time surface of the sim.  This amounts to comparing the
middle-left and middle-right panels in each of
Figures~\ref{fig:6941}--\ref{fig:7022}, and similarly for the other 111
models.

\begin{table}\centering\begin{tabular}{lrr}\hline
    Total                                                     & 119        & 100\%        \\
\hline
    errors in image locations          &     9         &    8\%            \\
    errors in image parities or time ordering     &    49     &    41\%     \\
\hline
    inaccurate image placement over an arc     &    21    &    18\%     \\
    identified two images of four                         &     5    &     4\% \\
    identified two nearby images as one & 3  & 3\%     \\
    missed faint images &   1   &  1\%     \\
    proposed too many images &  1  &  1\%    \\
    modelled a three-image arc as one image  &  4  &   3\%   \\
    modelled one image as a three-image arc  &  5  &   4\%   \\
    swapped minimum and saddle in double       &  2  &    2\%   \\
    swapped minima and saddles in quad            & 38 & 32\%   \\
    swapped early and late saddles in a quad &   7 &   6\%    \\
\hline
\end{tabular}
\caption{Table of image-identification errors and the number of models
  containing each.  A model can contain more than one type of error.}
\label{tab:stats}
\end{table}

@@

The assignment of the parity of the images was a more difficult task,
and was successful in only about 60\% of the cases.  The most common
error was swapping of minima and saddle-points in a quad;
\figref{7025} shows an example.  Another, less common, error was
flipping the spaghetti diagram, thus swapping the time-ordering of the
two saddle points.

Incorrect image parities and time orderings tended to produce
poorer-looking models, such as the checker board patterns in the mass
map in \figref{7025}.  Interestingly, however, the enclosed-mass
profiles were quite robust.  We will consider this aspect in the next
section.

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/eR_5}
  \caption{Model-recovered versus actual Einstein radii \ERf[,rec] and
    \ERf[,act].
    Plus signs indicate models flagged by the modeller as
    failures by commenting negatively about it in the forum. Light and dark grey
    bands show standard deviation of volunteers (15\%) and expert (10\%).}
  \label{fig:ER_per_sim}
\end{figure*}
